---
output: 
  github_document: 
    html_preview: false
  html_document: 
    theme:
      bootswatch: minty
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_dir = ".", output_format = "all", output_file = c("README.md", "index.html")) })
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  comment = "#>"
)
```

## drat

<!-- badges: start -->
<!-- badges: end -->

This repo uses Dirk Eddelbuettel's excellent `drat` package for creating a personalised CRAN-like repository.

**Setup**

First install `drat` using the usual method, then run `drat::addRepo("hfshr")` to add this repository to your list of urls.

```
# install.packages("drat")
drat::addRepo("hfshr")
```

**Usage**

You can now install any of my packages that are not available on CRAN using `install.packages()`, or update one of these packages with `update.packages()`.


**Available packages**

Last updated: `r Sys.time()`

```{r}

knitr::kable(
  as.data.frame(
    as.matrix(
      available.packages(repos = "https://hfshr.github.io/drat")[,c(1,2,15)] 
    ), row.names = FALSE)
)

```



